Assignment 3

### 2015-02-17 rmtw/a3/latex8.tex
Added interview and spell check

Give a clear introduction to what we mean by different paradigms. Just introduce manual/mdsd and the difference.

give examples of what we mean by changes, i.e. implementing scrum, TDD.

@@

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?
SRQ1: What are the challenges of implementing change in multi-paradigm environments?
SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?

@@

Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson. The EPG department consists of approximately 700 employees, the majority of hwich work on software development related tasks. EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}. The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}. The EPG product is utilized in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.

The company was sampled through convenience sampling, and a maximum varation strategy was used. As such, the goal was to include as many companies as possible in this study. Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.

@@

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias. The random sampling was done on official employee records. The number of subjects for the interviews was (XXX or were?) 15. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed. The main reason the three different roles were included was to be able to reduce reserach bias through data triangulation.

The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department. 5 years expirence was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson. The reason only employees from EPG were accepted was to ensure that the population was cohesive.

@@

\Section{Acknowledgements}
Write who did what

>>>>

@@

\SubSection{Research Question(s)}
RQ: How is change managed in multi-paradigm environments?

SRQ1: What are the challenges of implementing change in multi-paradigm environments?

SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?

SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?

@@

Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson. The EPG department consists of approximately 700 employees, the majority of which work on software development related tasks. EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}. The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}. The EPG product is utilised in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.

The company was sampled through convenience sampling, and a maximum variation strategy was used. As such, the goal was to include as many companies as possible in this study. Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.

@@

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias. The random sampling was done on official employee records. The number of subjects for the interviews was (XXX or were?) 15. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed. The main reason the three different roles were included was to be able to reduce research bias through data triangulation.

The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department. 5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson. The reason only employees from EPG were accepted was to ensure that the population was cohesive.

@@

\Section{Acknowledgements}
John had the main responsibility for sections 1 \& 2. William had the main responsibility for section 3. Section 4 and the interview questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.

We have re-used some material from our DIT037 course. (Mostly in literature review and case company description). Because of this some of the text might show up on Urkund. For the most important parts, such as methodology and research questions we have not used any material from our DIT035 paper.

\newpage
\appendix

\section{Interview Questions}
\begin{itemize}
\item \textbf{Organisation}
\begin{itemize}
\item How long have you worked at Ericsson?
\item How would you describe your role?
\item Do you work in a manual coding or MDSD team?
\end{itemize}

\item \textbf{General Change}
\begin{itemize}
\item Do you feel that the changes in Ericsson have had a clear plan?
\item How have the goals of the changes been communicated? 
\item What has been the largest obstacle for change?
\item What has been the main driving for change previously?
\item Do you feel that some previously introduced changes do not work well together?
\item Do you feel that the changes are targeted towards individuals or teams? 
\item If you have had previous experience of changes, how is change at Ericsson different? 
\end{itemize}

\item \textbf{Multi-paradigm Change}
\begin{itemize}
\item Do you feel that changes are implemented differently based on what development paradigm is used?
\item Do you feel that the implemented changes work well with both paradigms? 
\item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
\end{itemize}

\end{itemize}
